Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Challenges section

The challenges of introducing programmability into existing storage systems: (1) Programmability while keeping storage system available, (2) Finding and factoring out hard-wired policies and optimizations, (3) Bugs that were hidden because mechanisms were only exercised according to hard-wired policies and not in their full generality they were thought of -- programmability into a storage system turned out to be a great debugging tool, (4) version control and propagation of updates throughout the system without interrupting production workloads, (5) ...

>>>>

Establishing the infrastructure for programmability into existing services and abstractions of distributed storage systems is challenging, even if one assumes that the source code of the storage system and the necessary expertise for understanding it is available:

\begin{itemized}

\item Storage systems are generally required to be highly available so that any complete restarts of the storage system to reprogram them is usually unacceptable.

\item Policies and optimizations are usually hard-wired into the services and one has to be careful when factoring them out not to introduce additional bugs.

\item Mechanisms that are only exercised according to hard-wired policies and not in their full generality have hidden bugs that are revealed as soon as those mechanisms are governed by different policies. In our experience introducing programmability into a storage system proved to be a great debugging tool.

\item Programmability, especially in live systems, implies changes that need to be carefully managed by the system itself, including versioning and propagation of those changes without affecting correctness.

\end{itemize}
